MA_Results

### 2022-05-24 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
added Iterative section

# Framework
The framework we have developed consists of a set of standards and supporting toolkit for implementing an open source youth mental health model.

## Standards
We have identified 15 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles that models are TIMELY:

@@

### Iterative Models
Performance - validity and usefulness

I2: Model code is version controlled

I1: Model code and data use semantic versioning

I3: Model code development uses continuous integration (CI) tools and test units to ensure each new version is quality assured

>>>>

# Framework
The framework we have developed consists of a set of standards and tools for implementing those standards.

## Standards
We have identified 15 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models TIMELY:

@@

### Iterative Models
To avoid OSHEMs going stale - losing validity and usefulness with time, they should be routinely updated. A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.  Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable. For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers. The online platform GitHub [@github2007] can make this version history accessible to anyone.

GitHub also provides continuous integration [@CI2017] tools that can help make code updates more reliable. OSHEM developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run GitHub continuous integration checks that each new version of a code library passes multiple quality tests. These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?, can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).

Adopting semantic versioning [@semver20xx] conventions can be an efficient way to provide users of model code and data with information about the potential importance of an update. For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development. Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention. Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data can reduce the risk that model revisions have unintended consequences on third party users. The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code.

I2: Model code is version controlled <!-- Was I2 -->

I3: Model code development uses continuous integration (CI) tools and test units to ensure each new version is quality assured <!-- Was I3 -->

I1: Model code and data use semantic versioning <!-- Was I1 -->
